Precise predictions for same-sign W-bosons scattering at the LHC

### 2018-02-20 Draft/acknowledgements.tex
Add ackn. for CS, change BONSAY description
- shame on you Marco for modifying my description ;-)

BB, AD, and MP acknowledge financial support by the
German Federal Ministry for Education and Research (BMBF) under
contract no.~05H15WWCA1 and the German Science Foundation (DFG) under
reference number DE 623/6-1.
%
AK acknowledges financial support by the Swiss National Science Foundation (SNF) under contract 200020-175595.
MR acknowledges funding from the European Union's Horizon 2020 research and innovation programme as part of the Marie Sklodowska-Curie Innovative Training Network MCnetITN3 (grant agreement no. 722104).
MZ is supported by the Netherlands National Organisation for Scientific Research (NWO),

>>>>

BB, AD, and MP acknowledge financial support by the
German Federal Ministry for Education and Research (BMBF) under
contract no.~05H15WWCA1 and the German Science Foundation (DFG) under
reference number DE 623/6-1.
%
AK acknowledges financial support by the Swiss National Science Foundation (SNF) under contract 200020-175595.
MR acknowledges funding from the European Union's Horizon 2020 research and innovation programme as part of the Marie Sklodowska-Curie Innovative Training Network MCnetITN3 (grant agreement no. 722104).
MZ is supported by the Netherlands National Organisation for Scientific Research (NWO),
CS acknowledges support by the state of Baden-W\"urttemberg through bwHPC and the German Research Foundation (DFG) through grant no INST 39/963-1 FUGG and grant DI 784/3.

### 2018-02-20 Draft/description.tex
Add ackn. for CS, change BONSAY description
- shame on you Marco for modifying my description ;-)

    \item The program {\sc Bonsay} consists of a general-purpose Monte Carlo integrator. It implements the VBS approximation at LO and NLO, with
        the exception of the virtual matrix elements, which are computed in the EVBA. Matrix elements are taken from several sources.
 Born matrix elements are adapted from the program {\sc Lusifer} \cite{Dittmaier:2002ap} for the partonic processes, real matrix elements are written by Marina Billoni, and virtual matrix elements by Stefan Dittmaier.
One loop integrals are evaluated using the {\sc Collier} library~\cite{Denner:2014gla,Denner:2016kdg}.

>>>>

\item The program {\sc Bonsay} consists of a general-purpose Monte Carlo integrator written by Christopher Schwan and matrix elements taken from different sources:
Born matrix elements are adapted from the program {\sc Lusifer}~\cite{Dittmaier:2002ap}, real matrix elements are written by Marina Billoni, and virtual matrix elements by Stefan Dittmaier.
One loop integrals are evaluated using the {\sc Collier} library~\cite{Denner:2014gla,Denner:2016kdg}.
For the fiducial cross sections it uses the VBS approximation at LO and NLO.
The virtuals are additionally approximated using a double pole approximation.
For more inclusive cross sections at LO the exact matrix elements ($s$-channels, interferences) are used.
